%-------------------------
% Resume in Latex
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{ #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://github.com/satyajeetramnit}{\Huge Satyajeet Ramnit}} &  \href{https://github.com/satyajeetramnit}{github.com/satyajeetramnit}\\
  \textbf{Purnea, Bihar} & \href{https://www.linkedin.com/in/satyajeet-ramnit-2708/}{linkedin.com/in/satyajeetramnit/} \\
  Ph. : \href{tel:+918210386150}{+91 8210386150} & Email : \href{mailto:satyajeetramnit2708@gmail.com}{satyajeetramnit2708@gmail.com} \\
\end{tabular*}

% \begin{center}
% 	{\Huge \scshape Satyajeet Ramnit} \\ \vspace{1pt}
% 	Purnea, Bihar \\ \vspace{1pt}
% 	\small \raisebox{-0.2\height}\faPhone\ Ph No.: +91 8210386150 ~ \href{x@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{satyajeetramnit2708@gmail.com}} ~
% 	\href{https://linkedin.com/in//}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/satyajeet-ramnit-2708/}}
% 	\vspace{-8pt}
% \end{center}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://kiit.ac.in/}{Kalinga Institute of Industrial Technology}}{Bhubaneshwar, India}
      {BTech in Information Technology;  \href{}{CGPA: 8.88}}{Jul. 2019 -- Jul. 2023}
    % \resumeSubheading
    %   {\href{https://ipspurnea.com/}{Indian Public School}}{Purnea, Bihar}
    %   {HSC/Intermediate;  \href{}{Percentage: 65.6}}{Apr. 2017 -- Mar. 2018}
    %  \resumeSubheading
    %   {\href{https://www.brightcareerschoolpurnea.com/}{Bright Career School}}{Purnea, Bihar}
    %   {SSC/Matriculation;  \href{}{CGPA: 10}}{Apr. 2015 -- Mar. 2016}
  \resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
	\small{\item{
		\textbf{Coursework}{: Data Structure and Algorithms, Object Oriented Programming, Problem Solving, DataBase Management System, Operating System.} \\
 	\textbf{Languages}{: C/C++, Python, Java, Jenkins, HTML/CSS, JavaScript, SQL, Flutter.} \\
%  		\textbf{Operating System}{: Windows, Linux}\\
%  	\textbf{Source Control}{: Git }\\
 		\textbf{Tools}{: Git, Docker, Visual Studio Code, IntelliJ IDEA, Figma, Adobe XD, Jupiter Notebook}\\
%  	\textbf{Technologies/Frameworks/Libraries}{: Node.js,ExpressJS, ReactJS.} \\
	}}
 \end{itemize}
 \vspace{-16pt}
 
 %

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {GE Healthcare}{Bengaluru, India}
      {Intern}{Oct. 2022 - Present}
      \resumeItemListStart
        \resumeItem{C++, Python, Docker, MR, CI/CD, Jenkins: }
          {Working on MR Imaging Domain to automate the debugging of AIRx Site Issue to reduce the developer's crucial time spent on debugging and setup.}
      \resumeItemListEnd

    \resumeSubheading
      {EPIKInDiFi}{Bhubaneswar, India}
      {Intern Trainee}{Jan. 2022 - Jun. 2022}
      \resumeItemListStart
        \resumeItem{Flutter, JavaScript, EDA, Linux: }
          {Are the tools and tech stacks I was trained on with hands-on experience.}
      \resumeItemListEnd
    \resumeSubHeadingListEnd
      
      
% --------Multiple Positions Heading------------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    % \resumeSubheading
      
%

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{\textbf{Code Dynamics} $|$ {\href{https://www.codedynamics.in/}{\bf View Project:}}}
      {Designed on \textbf{Figma}. Tech stacks: \textbf{NextJS}, and \textbf{Tailwind CSS}. Base design features: \textbf{Glassmorphism} & \textbf{neomorphism}. For resources of all major coding platforms and different coding sheets.}
    \resumeSubItem{\textbf{Bus Booking Management System} $|$ {\href{https://github.com/AnkitRajCode/Bus-Booking-Management-System}{\bf View Project:}}}
      {Designed on \textbf{Figma}. Tech stacks: \textbf{Firebase}, and \textbf{Tailwind CSS}. A software solution to simplify the ticket booking and purchasing process for customers.}
    \resumeSubItem{\textbf{Library Management System} $|$ {\href{https://satyajeetramnit.github.io/Library-Management-System/}{\bf View Project:}}}
      {Simple BookClub database that is maintaining a list of books, who has lent the book, and who has borrowed the book. We can also add new book entries, and borrow and return books.}
    \resumeSubItem{\textbf{EDA - Agent Bonus (Life Insurance Company)} $|$ {\href{https://github.com/satyajeetramnit/Data-Science-Projects/tree/main/Agent-Bonus-Life-Insurance_Company}{\bf View Project:}}}
      {Dataset belongs to a life insurance company. The company wants to predict the bonus for its agents so that it may design appropriate engagement activities.}
  \resumeSubHeadingListEnd


%-----------Achievements-----------
\section{Achievements}
%  \begin{itemize}[leftmargin=0.15in, label={}]
% 	\resumeItemListStart
 \resumeSubHeadingListStart
    	\resumeItem{Highest rating of \textbf{1758} at {\href{https://codechef.com/users/ramnit_code_27}{\bf Codechef}, and rated \textbf{3*}, also *242 and \textbf{*282} Global Rank in \href{https://www.codechef.com/AUG21C}{August Challenge 2021} and \href{https://www.codechef.com/START7C}{CodeChef Starters 7} respectively.}}
    	
    	\resumeItem{5* Badge in C, C++, DSA, 4* Badge In Java, 3* in SQL and Python on  {\href{https://www.hackerrank.com/satyajeetramnit1?hr_r=1}{\bf Hackerrank.}}}
%   	\resumeItemListEnd
 \resumeSubHeadingListEnd
%  \end{itemize}
%  \vspace{-16pt}
 %
 

%-----------Certifications & Profile Links-----------
\section{Certifications and Profile Links}
 \begin{itemize}[leftmargin=0.15in, label={}]
	\small{\item{
		\href{https://www.hackerrank.com/certificates/a64619ef6646}{\textbf{Hackerrank Certifications}{: Problem Solving, Java, SQL & Python.}} \\
 	    \href{https://www.udemy.com/certificate/UC-1adcc95f-c44b-49e7-8a39-75b9e84a3350/}{\textbf{Web Developer BootCamp}} \\
 	    \href{https://drive.google.com/file/d/1gAJfSQNtBdIQe9vkkxHTb0J2uGw_tLmb/view}{\textbf{KIIT International e-MUN}{: Officer (Design Dept.)}} \\
 	    \  \ \\
 	    \textbf{Profile Links :}{ $|$ \href{https://leetcode.com/satyajeetramnit2708/}{{Leetcode}} $|$ \href{https://www.hackerrank.com/satyajeetramnit1?hr_r=1}{{Hackerrank}} $|$ \href{https://www.codechef.com/users/ramnit_code_27}{{Codechef}} $|$ \href{https://auth.geeksforgeeks.org/user/satyajeetramnit27/practice/}{{GeeksForGeeks}} $|$} \\
	}}
 \end{itemize}
 \vspace{-16pt}


% --------Organisations------------
\section{Organisations}
\resumeSubHeadingListStart
  \resumeSubheading
      {Next Gen UI}{India}
      {UI/UX - FrontEnd Developer}{Dec. 2021 - Present}
    %   \resumeItemListStart
    %     \resumeItem{Flutter, JavaScript, Python, EDA, Linux}
    %       {Were among the tools and tech. I worked on out of which few were learnt from scratch by building different basic projects through it.}
    %   \resumeItemListEnd
    \resumeSubheading
      {GfG Chapter KIIT}{Bhubaneswar, India}
      {UI/UX Designer}{Nov. 2020 - Jun. 2021}
    \resumeSubheading
      {National Service Scheme (NSS)}{Bhubaneswar, India}
      {Volunteer}{Dec. 2020 - Aug 2021}
\resumeSubHeadingListEnd




%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}

\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{} $|$ {\href{https://www.codedynamics.in/}{\bf View Project:}}}
      {Designed this project from scratch on \textbf{Figma}. The tech stacks used are \textbf{NextJS}, and \textbf{Tailwind CSS}. \textbf{Glassmorphism} & \textbf{neomorphic} are the base design features.}
    \resumeSubItem{\textbf{Library Management System} $|$ {\href{https://satyajeetramnit.github.io/Library-Management-System/}{\bf View Project:}}}
      {Simple BookClub database that is maintaining a list of books, who has lent the book, and who has borrowed the book. We can also add new book entries, and borrow and return books.}
    \resumeSubItem{\textbf{EDA - Agent Bonus (Life Insurance Company)} $|$ {\href{https://github.com/satyajeetramnit/Data-Science-Projects/tree/main/Agent-Bonus-Life-Insurance_Company}{\bf View Project:}}}
      {Dataset belongs to a life insurance company. The company wants to predict the bonus for its agents so that it may design appropriate engagement activities.}
  \resumeSubHeadingListEnd